\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Problem 20}
Iz skupa od 10 studenata, među kojima su samo jedan student elektrotehnike i samo jedan student matematike, biramo komisiju od 6 članova, ali tako da ako je u komisiji student elektrotehnike mora u toj komisiji biti i student matematike. Koliko se takvih komisija može obrazovati?
\begin{enumerate}
    \item[(A)] $210$
    \item[(B)] $98$
    \item[(C)] $126$
    \item[(D)] $154$
    \item[(E)] $165$
    \item[(N)] Ne znam
\end{enumerate}

\subsection*{Solution}
Let $E$ be the student of electrotechnics and $M$ be the student of mathematics.
There are 8 other students ($O_1, \dots, O_8$). Total 10 students.
We need to choose 6 members.
The condition is: If $E$ is chosen, then $M$ must be chosen.
This means we cannot have a committee with $E$ but without $M$.
The possible valid compositions are:
1. Neither $E$ nor $M$ is in the committee. (Impossible, we need 6 from 8, ok)
   Wait, "if E then M" implies:
   - E is NOT in (M can be in or not).
   - E IS in (M must be in).
   So invalid case is: E is in AND M is NOT in.
   
Let's count by cases:
Case 1: $E$ is not in the committee.
We choose 6 members from the remaining 9 students ($M$ + 8 others).
\[
\binom{9}{6} = \binom{9}{3} = \frac{9 \cdot 8 \cdot 7}{3 \cdot 2 \cdot 1} = 3 \cdot 4 \cdot 7 = 84
\]

Case 2: $E$ is in the committee.
Then $M$ must also be in the committee.
We have chosen $E$ and $M$ (2 members). We need to choose $6-2=4$ more members from the remaining 8 students ($O_1, \dots, O_8$).
\[
\binom{8}{4} = \frac{8 \cdot 7 \cdot 6 \cdot 5}{4 \cdot 3 \cdot 2 \cdot 1} = 70
\]

Total valid ways = $84 + 70 = 154$.

Alternatively, Total ways to choose 6 from 10 is $\binom{10}{6} = \binom{10}{4} = \frac{10 \cdot 9 \cdot 8 \cdot 7}{24} = 210$.
Subtract invalid cases: E is in, M is not.
If E is in and M is out, we need to choose 5 more from the 8 others.
\[
\binom{8}{5} = \binom{8}{3} = \frac{8 \cdot 7 \cdot 6}{6} = 56
\]
Valid ways = $210 - 56 = 154$.

\subsection*{Answer}
$154$ (option \textbf{(D)}).

\end{document}