\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Problem 13}
Osnovna ivica pravilne četvorostrane piramide je 8 cm, a središte osnove je od bočne strane na rastojanju 2 cm. Tada je visina piramide jednaka:

\subsection*{Solution}
Let the regular square pyramid have:
\begin{itemize}
\item Base edge $a = 8$ cm
\item Distance from center of base to lateral face $d = 2$ cm
\end{itemize}

For a regular square pyramid, the distance from the center of the base to the midpoint of a base edge is called the apothem of the base:
\[
r = \frac{a}{2} = \frac{8}{2} = 4 \text{ cm}
\]

The distance from the center of the base to a lateral face is the apothem of the pyramid (the perpendicular distance from the center to the slant face).

Let $h$ be the height of the pyramid and $h_s$ be the slant height (height of the triangular face from base edge to apex).

The apothem of the pyramid $a_p$ relates to these by:
In the right triangle formed by the height $h$, the apothem of the base $r = 4$, and the slant height $h_s$:
\[
h_s = \sqrt{h^2 + r^2} = \sqrt{h^2 + 16}
\]

The distance from the center of the base to a lateral face can be found using the formula. Consider the triangle formed by the apex, the center of the base, and the midpoint of a base edge. The area of this triangle can be computed two ways.

Actually, the perpendicular distance from the center of the base to the slant face is:
\[
d = \frac{h \cdot r}{\sqrt{h^2 + r^2}}
\]

Wait, let me reconsider. The distance from a point to a plane in 3D...

The lateral face passes through a base edge and the apex. The perpendicular from the center of the base to this face has length 2 cm.

Using the formula for the distance from center to slant face:
\[
d = \frac{h \cdot r}{h_s} = \frac{h \cdot r}{\sqrt{h^2 + r^2}}
\]

With $d = 2$ and $r = 4$:
\[
2 = \frac{4h}{\sqrt{h^2 + 16}}
\]
\[
2\sqrt{h^2 + 16} = 4h
\]
\[
\sqrt{h^2 + 16} = 2h
\]
\[
h^2 + 16 = 4h^2
\]
\[
16 = 3h^2
\]
\[
h^2 = \frac{16}{3}
\]
\[
h = \frac{4}{\sqrt{3}} = \frac{4\sqrt{3}}{3} \text{ cm}
\]

\subsection*{Answer}
$\dfrac{4\sqrt{3}}{3}$ cm (option \textbf{D}).

\end{document}
