\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Problem 20}
Iz skupa od 10 studenata, među kojima su samo jedan student elektrotehnike i samo jedan student matematike, biramo komisiju od 6 članova, ali tako da ako je u komisiji student elektrotehnike mora u toj komisiji biti i student matematike. Koliko se takvih komisija može obrazovati?

(A) $210$ \quad (B) $98$ \quad (C) $126$ \quad (D) $154$ \quad (E) $165$ \quad (N) Ne znam

\subsection*{Solution}
Let $E$ denote the electrical engineering student and $M$ denote the mathematics student.

We need to count committees where: if $E$ is in the committee, then $M$ must also be in the committee.

This is equivalent to: NOT ($E$ in committee AND $M$ not in committee).

Total ways to choose 6 from 10: $\binom{10}{6} = 210$

Invalid committees: $E$ is in but $M$ is not.
- $E$ is in the committee (1 way)
- $M$ is not in the committee
- Choose remaining 5 members from the other 8 students (excluding both $E$ and $M$): $\binom{8}{5} = 56$

Valid committees = Total - Invalid = $210 - 56 = 154$

\textbf{Alternative approach:}

Case 1: Neither $E$ nor $M$ is in the committee.
Choose 6 from the remaining 8: $\binom{8}{6} = 28$

Case 2: Both $E$ and $M$ are in the committee.
Choose remaining 4 from the other 8: $\binom{8}{4} = 70$

Case 3: $M$ is in but $E$ is not.
Choose remaining 5 from the other 8: $\binom{8}{5} = 56$

Total valid = $28 + 70 + 56 = 154$

\subsection*{Answer}
$154$ (option \textbf{D}).

\end{document}
