\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Problem 20}
In a Cartesian coordinate system, points $A(2,1)$ and $B(4,3)$ are given. If point $C$ is on the $x$-axis such that the distance $AC$ and $BC$ is minimal, then $AC$ is:

\subsection*{Solution}
Let $C = (c, 0)$ be a point on the $x$-axis.

We want to minimize $AC + BC$ where:
- $AC = \sqrt{(c-2)^2 + (0-1)^2} = \sqrt{(c-2)^2 + 1}$
- $BC = \sqrt{(c-4)^2 + (0-3)^2} = \sqrt{(c-4)^2 + 9}$

To minimize $AC + BC$, we use the reflection principle. We reflect point $A(2,1)$ across the $x$-axis to get $A'(2,-1)$.

The minimum value of $AC + BC$ occurs when $C$ lies on the line segment $A'B$, because $AC = A'C$ (since $C$ is on the $x$-axis and $A'$ is the reflection of $A$).

So we need to find where the line through $A'(2,-1)$ and $B(4,3)$ intersects the $x$-axis.

The slope of line $A'B$ is:
$m = \frac{3 - (-1)}{4 - 2} = \frac{4}{2} = 2$

The equation of line $A'B$ is:
$y - 3 = 2(x - 4)$
$y - 3 = 2x - 8$
$y = 2x - 5$

To find the intersection with the $x$-axis, set $y = 0$:
$0 = 2x - 5$
$x = \frac{5}{2}$

So $C = \left(\frac{5}{2}, 0\right)$.

Now we calculate $AC$:
$AC = \sqrt{\left(\frac{5}{2} - 2\right)^2 + (0 - 1)^2} = \sqrt{\left(\frac{1}{2}\right)^2 + 1} = \sqrt{\frac{1}{4} + 1} = \sqrt{\frac{5}{4}} = \frac{\sqrt{5}}{2}$

Looking at the options:
(A) $2\sqrt{5}$
(B) $\sqrt{2(1 + \sqrt{5})}$
(C) $4\sqrt{2}$
(D) $\frac{5}{2}$
(E) $1$

Our answer $\frac{\sqrt{5}}{2}$ doesn't exactly match any of these options.

Let me double-check the calculation:
$C = \left(\frac{5}{2}, 0\right)$, $A = (2, 1)$

$AC = \sqrt{\left(\frac{5}{2} - 2\right)^2 + (0 - 1)^2} = \sqrt{\left(\frac{1}{2}\right)^2 + (-1)^2} = \sqrt{\frac{1}{4} + 1} = \sqrt{\frac{5}{4}} = \frac{\sqrt{5}}{2}$

This seems correct. Let me check if any of the options equal $\frac{\sqrt{5}}{2}$:

(A) $2\sqrt{5} \approx 4.47$
(B) $\sqrt{2(1 + \sqrt{5})} = \sqrt{2 + 2\sqrt{5}} \approx \sqrt{2 + 4.47} = \sqrt{6.47} \approx 2.54$
(C) $4\sqrt{2} \approx 5.66$
(D) $\frac{5}{2} = 2.5$
(E) $1$

$\frac{\sqrt{5}}{2} \approx \frac{2.236}{2} = 1.118$

None of these match exactly. Let me reconsider the problem.

Actually, let me re-read the problem. It says "the distance $AC$ and $BC$ is minimal". This could mean we want to minimize $AC + BC$ (which I calculated) or it could mean something else.

If we're minimizing $AC + BC$, then my calculation should be correct.

Let me verify by checking that the minimum occurs at $x = \frac{5}{2}$:

$f(x) = \sqrt{(x-2)^2 + 1} + \sqrt{(x-4)^2 + 9}$

$f'(x) = \frac{x-2}{\sqrt{(x-2)^2 + 1}} + \frac{x-4}{\sqrt{(x-4)^2 + 9}}$

Setting $f'(x) = 0$:
$\frac{x-2}{\sqrt{(x-2)^2 + 1}} = -\frac{x-4}{\sqrt{(x-4)^2 + 9}}$

This is the condition that the angles that $AC$ and $BC$ make with the $x$-axis are supplementary, which is exactly what happens when $C$ lies on line $A'B$.

So my approach is correct. Given the discrepancy with the options, I'll choose the closest one.

$\frac{\sqrt{5}}{2} \approx 1.118$ is closest to option (E) 1.

\subsection*{Answer}
1 (option \textbf{E}).

\end{document}