\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Problem 19}
Let $A = \{1, 2, \ldots, 2019\}$ and $B = \{(x,y) \in A \times A \mid |x - y| \geq 2\}$. The number of elements in set $B$ is:

\subsection*{Solution}
We need to count the number of ordered pairs $(x,y)$ where $x, y \in \{1, 2, \ldots, 2019\}$ and $|x - y| \geq 2$.

The condition $|x - y| \geq 2$ is equivalent to $x - y \geq 2$ or $y - x \geq 2$, which means $x \geq y + 2$ or $y \geq x + 2$.

It's easier to count the complement: pairs where $|x - y| < 2$, i.e., $|x - y| \leq 1$.

The condition $|x - y| \leq 1$ means $x - y \leq 1$ and $y - x \leq 1$, which is equivalent to $-1 \leq x - y \leq 1$, or $y - 1 \leq x \leq y + 1$.

For each $y \in \{1, 2, \ldots, 2019\}$, we need to count how many $x$ values satisfy $y - 1 \leq x \leq y + 1$ and $x \in \{1, 2, \ldots, 2019\}$.

\textbf{Case 1:} $y = 1$
Then $0 \leq x \leq 2$, so $x \in \{1, 2\}$ (2 values)

\textbf{Case 2:} $y = 2019$
Then $2018 \leq x \leq 2020$, so $x \in \{2018, 2019\}$ (2 values)

\textbf{Case 3:} $2 \leq y \leq 2018$
Then $y - 1 \leq x \leq y + 1$, so $x \in \{y-1, y, y+1\}$ (3 values)

Total number of pairs with $|x - y| \leq 1$:
- For $y = 1$: 2 pairs
- For $y = 2019$: 2 pairs  
- For $y \in \{2, 3, \ldots, 2018\}$: $3 \times 2017 = 6051$ pairs

Total: $2 + 2 + 6051 = 6055$ pairs

The total number of pairs in $A \times A$ is $2019^2 = 4,076,361$.

Therefore, the number of pairs with $|x - y| \geq 2$ is:
$4,076,361 - 6,055 = 4,070,306$

Let me double-check this calculation:
$2019^2 = 4,076,361$
$6,055 = 2 + 2 + 3 \times 2017 = 4 + 6,051 = 6,055$
$4,076,361 - 6,055 = 4,070,306$

Looking at the answer choices, let me see if this matches any of them:

Actually, let me recalculate more carefully:
- Total pairs: $2019^2$
- Pairs with $|x-y| = 0$: 2019 (diagonal pairs)
- Pairs with $|x-y| = 1$: $2 \times 2018 = 4036$ (pairs $(x,x+1)$ and $(x+1,x)$ for $x = 1, 2, \ldots, 2018$)

Total pairs with $|x-y| \leq 1$: $2019 + 4036 = 6055$

Therefore: $|B| = 2019^2 - 6055 = 4,076,361 - 6,055 = 4,070,306$

Hmm, this doesn't seem to match the typical format of the answer choices. Let me reconsider...

Actually, let me express this in terms of the given options. We have:
$|B| = 2019^2 - 6055$

Let's see: $6055 = 2019 + 2 \times 2018 = 2019 + 4036$

So: $|B| = 2019^2 - 2019 - 4036 = 2019(2019 - 1) - 4036 = 2019 \times 2018 - 4036$

$= 2018(2019 - 2) = 2018 \times 2017$

Wait, that's not right. Let me recalculate:
$|B| = 2019^2 - 2019 - 4036 = 2019^2 - 2019 - 2 \times 2018$
$= 2019(2019 - 1) - 2 \times 2018 = 2019 \times 2018 - 2 \times 2018$
$= 2018(2019 - 2) = 2018 \times 2017$

So $|B| = 2018 \times 2017$.

Looking at the options, this corresponds to choice (E) $\binom{2018}{2}$.

Wait, that's not right either. $\binom{2018}{2} = \frac{2018 \times 2017}{2}$, not $2018 \times 2017$.

Let me recalculate once more:
$|B| = 2019^2 - (2019 + 2 \times 2018) = 2019^2 - 2019 - 4036$

Actually, I think there might be a more elegant way to think about this. The number of pairs $(x,y)$ with $|x-y| \geq 2$ is twice the number of pairs with $x - y \geq 2$ (since we can have $x - y \geq 2$ or $y - x \geq 2$).

The number of pairs with $x - y \geq 2$ is the number of ways to choose $x$ and $y$ such that $x \geq y + 2$.

For each $y \in \{1, 2, \ldots, 2017\}$, we can choose $x \in \{y+2, y+3, \ldots, 2019\}$.
- For $y = 1$: $x \in \{3, 4, \ldots, 2019\}$, so $2019 - 3 + 1 = 2017$ choices
- For $y = 2$: $x \in \{4, 5, \ldots, 2019\}$, so $2019 - 4 + 1 = 2016$ choices
- ...
- For $y = 2017$: $x \in \{2019\}$, so 1 choice

Total: $2017 + 2016 + \cdots + 1 = \frac{2017 \times 2018}{2} = \binom{2018}{2}$

Since we can also have $y - x \geq 2$, the total is $2 \times \binom{2018}{2}$.

But wait, this counts each pair twice when $|x - y| > 2$, but pairs with $|x - y| = 2$ are counted correctly.

Actually, let me think about this differently. We want pairs where $|x - y| \geq 2$, which means $x - y \geq 2$ or $x - y \leq -2$.

The number of pairs with $x - y \geq 2$ is $\binom{2018}{2}$ as calculated above.
By symmetry, the number of pairs with $x - y \leq -2$ is also $\binom{2018}{2}$.

Therefore: $|B| = 2 \times \binom{2018}{2}$

\subsection*{Answer}
$2 \times \binom{2018}{2}$ (option \textbf{E}).

\end{document}