\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Problem 12}
The set of solutions of the inequality $x + 2 < \sqrt{x + 44}$ is (for some real numbers $a, b, c, d$ such that $-\infty < a < b < c < d < +\infty$):

\subsection*{Solution}
We need to solve $x + 2 < \sqrt{x + 44}$.

First, we need the domain: $x + 44 \geq 0 \Rightarrow x \geq -44$.

Case 1: $x + 2 \geq 0$ (i.e., $x \geq -2$)
We can square both sides:
\[
(x + 2)^2 < x + 44
\]
\[
x^2 + 4x + 4 < x + 44
\]
\[
x^2 + 3x - 40 < 0
\]
\[
(x + 8)(x - 5) < 0
\]

This gives us $-8 < x < 5$.

Since we're in Case 1 where $x \geq -2$, we get $-2 \leq x < 5$.

Case 2: $x + 2 < 0$ (i.e., $x < -2$)
In this case, the left side is negative while the right side $\sqrt{x + 44}$ is always non-negative (when defined). So the inequality is automatically satisfied.

We need $x \geq -44$ (domain condition) and $x < -2$, so we get $-44 \leq x < -2$.

Combining both cases:
- From Case 1: $-2 \leq x < 5$
- From Case 2: $-44 \leq x < -2$

Therefore, the solution is $-44 \leq x < 5$, which can be written as $[-44, 5)$.

Let's verify the boundary points:
- At $x = -44$: $-44 + 2 = -42$ and $\sqrt{-44 + 44} = 0$. Since $-42 < 0$, the inequality holds.
- At $x = 5$: $5 + 2 = 7$ and $\sqrt{5 + 44} = \sqrt{49} = 7$. Since $7 \not< 7$, the inequality doesn't hold.
- At $x = -2$: $-2 + 2 = 0$ and $\sqrt{-2 + 44} = \sqrt{42} > 0$. Since $0 < \sqrt{42}$, the inequality holds.

\subsection*{Answer}
$[d, +\infty)$ - Wait, let me recalculate. The answer should be $(-\infty, b] \cup [c, +\infty)$ format.

Actually, looking at our solution $[-44, 5)$, this corresponds to option \textbf{E} $[d, +\infty)$ where we interpret this as a single interval.

But looking more carefully at the options, our interval $[-44, 5)$ doesn't match the given formats exactly. Let me check option \textbf{C} $(a, b) \cup [c, +\infty)$.

\subsection*{Answer}
$(a, b) \cup [c, +\infty)$ (option \textbf{C}).

\end{document}